---
title: "multimedia"
output: md_document
---

# miniLNM

```{r, setup, message = FALSE}
library(miniLNM)
library(dplyr)
```

miniLNM is a lightweight package for fitting and using logistic-normal multinomial
models. It wraps a simple Stan script (see  `inst/stan/` folder in the [source code](https://github.com/krisrs1128/miniLNM))
and defines an S4 class that makes it easy to specify, estimate, and draw
samples from the fit. For example, you can use tidyselect syntax to relate
multiple compositional outputs to a set of influential biological factors.

```{r}
example_data <- lnm_data()
xy <- bind_cols(example_data[c("X", "y")])
fit <- lnm(starts_with("y") ~ starts_with("x"), xy)
```

The print method gives a concise summary of the fitted model, which is easier to
read than the full Stan output.

```{r}
fit
```

You can also use `predict`, like in ordinary linear models, and can draw
posterior predictive samples using `sample`.

```{r}
p_hat <- predict(fit)
y_star <- sample(fit, depth = 200)
```

### Help

We welcome questions and comments about the package either through [github](https://github.com/krisrs1128/miniLNM/issues) or [email](ksankaran@wisc.edu).

