---
title: "demo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(miniLNM)
library(tidyverse)
set.seed(20240904)
```

This vignette illustrates use of the `lnm` function using a simulated dataset.
First, we create some example data coming from a true LNM model.

```{r}
example_data <- lnm_data(N = 200, K = 20)
xy <- bind_cols(example_data[c("X", "y")])
```

Next, we define the regression. We are using an extension of the formula
interface that allows for multiple outcomes. This allows us to use it for a
wider range of integration problems, like in our multimedia package for
mediation analysis.

```{r}
fit <- lnm(starts_with("y") ~ starts_with("x"), xy)
```

Once we have estimated the model, we can use predict to get the fitted
compositions on the training data. We can also draw new samples at different
read depths and use `newdata` to sample at new design points.

```{r}
newx <- lnm_data()$X
new_p_hat <- predict(fit, newx, depth = 300)
```

Let's verify that the estimates are close to the truth. First we'll get some
fitted values.

```{r}
p_hat <- predict(fit, example_data$X)
y_star <- sample(fit, newdata = example_data$X, depth = 1e4)
```

And now we plot it. So, despite the diagnostic warning from above, the estimates
seem pretty good.

```{r}
true <- colMeans(example_data$y / rowSums(example_data$y))
fitted <- colMeans(y_star / rowSums(y_star))
plot(true, colMeans(p_hat), asp = 1)
points(true, fitted, col = "red")
abline(a = 0, b = 1)
```
